### 2023-09-06 main.tex
Fix 5
kj
lk
W exact draft

@@

\langle n^{x_{1}}_{a_{1}}\cdots n^{x_{m}}_{a_{m}}\rangle_{\text{stat}}=\sum_{t_{1},\ldots,t_{m}=0}^{1}
\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,x_{q},c_{q},\ldots,c_{m})\alpha_{a_{q}}^{t_{q}}\beta_{a_{q}}^{1-t_{q}}

@@

%blue} In case of a chain $L=2$ and $N=3$ and choosing $i=2$ this reads as 
%\begin{equation*}
%	D_{22}^{2L-1}=6e_{22}^{tot}+e_{11}^{tot}-e_{22}^{tot}-e_{33}^{tot}-2e_{22}^{tot}e_{22}^{tot}-2e_{23}^{tot}e_{32}^{tot}
%\end{equation*}
%where
%\begin{equation*}
%	e_{ab}^{tot}=e_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes e_{ab}\qquad \forall a,b\in \{1,2,3\}
%\end{equation*}
%This gives exactly
%\begin{equation*}
%	D_{22}^{2L-1}=\left(
%	\begin{array}{ccccccccc}
%		2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 2 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & -2 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & -2 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & -2 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & -2 \\
%	\end{array}
%	\right)
%\end{equation*}
%}
%\textbf{Observation}: it seems to me that, although not diagonal, the $D_{ii}^{2L-1}$ does not chaing the exitation of the chain since we have $e_{ij}^{tot}e_{ji}^{tot}$!\\
%The following \textit{lower diagonal} elements of $U_{0}(x)$, $\forall i=2,\ldots,L$ and for $j=1$
%\begin{equation}
%	C_{i}(x)=C_{i}^{2L-1}x^{2L-1}+\ldots
%\end{equation}
%where the coefficient is
%\begin{equation}\label{c}
%	C_{i}^{2L-1}=2e_{1i}^{tot}+2\sum_{a< b}\left(e_{1i}^{[a]}e_{11}^{[b]}-e_{1i}^{[a]}e_{ii}^{[b]}-\sum_{a=2\,:\,k\neq j}^{N}e_{1a}^{[a]}e_{ai}^{[b]}\right)
%\end{equation}
\item For $B_{j}(x)$  $\forall j=2,\ldots,L$ 
\begin{equation}\label{B-charge}
		B_{j}^{2L-1}=	2e_{j1}^{tot}e_{11}^{tot}-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=1}^{N} e_{jk}^{[a]}e_{k1}^{[b]}
\end{equation}
\begin{comment}
\begin{equation}
B_{j}(x)=B_{j}^{2L-1}x^{2L-1}+\ldots
\end{equation}
where the coefficient is 
\begin{equation}\label{b}
\begin{split}
B_{j}^{2L-1}&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-e_{j1}^{[a]}e_{jj}^{[b]}-\sum_{k=2\,:\,k\neq j}^{N}e_{k1}^{[a]}e_{jk}^{[b]}\right)\\
&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-\sum_{k=2}^{N}e_{k1}^{[a]}e_{jk}^{[b]}\right)
\end{split}
\end{equation}
then
\begin{equation}
\begin{split}
B_{j}^{2L-1}=2e_{j1}^{tot}+
2\sum_{a,b=1\,:\, a<b}^{L}\left(e_{j1}^{[a]}e_{11}^{[b]}\right)-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=2}^{N}\left( e_{jk}^{[a]}e_{k1}^{[b]}\right)
\end{split}
\end{equation}
\begin{equation}
\begin{split}
B_{j}^{2L-1}&=
2\sum_{a,b=1}^{L}\left(e_{j1}^{[a]}e_{11}^{[b]}\right)-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=1}^{N}\left( e_{jk}^{[a]}e_{k1}^{[b]}\right)\\
%	&=
%	2e_{j1}^{tot}e_{11}^{tot}-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=1}^{N} e_{jk}^{[a]}e_{k1}^{[b]}
\end{split}
\end{equation}
Thus
\begin{equation}
\boxed{	B_{j}^{2L-1}=	2e_{j1}^{tot}e_{11}^{tot}-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=1}^{N} e_{jk}^{[a]}e_{k1}^{[b]}}
\end{equation}
\end{comment}
\item For $D_{i,j}(x)$ with $i,j=2,\ldots,N$ such that $i\neq j$
\begin{equation}
D_{i,j}^{2L}=-2e_{ji}^{tot}
\end{equation}
\end{itemize}
\textbf{Remark}: it is easy to see that, when restricted to the case of 2 species,  \eqref{a2lp},\eqref{a2l},\eqref{a2lm1} correspond to the one compute in \cite{frassek2020eigenstates}. \\ \\
The interesting charges (we only look for the first non trivial one) take the following form

@@

@@

>>>>

\langle n^{x_{1}}_{a_{1}}\cdots n^{x_{m}}_{a_{m}}\rangle_{\text{stat}}=&\sum_{c_{1},\ldots,c_{m}=0}^{1}

@@

\langle n^{x_{1}}_{a_{1}}\cdots n^{x_{m}}_{a_{m}}\rangle_{\text{stat}}=&\sum_{t_{1},\ldots,t_{m}=0}^{1}
\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,x_{q},c_{q},\ldots,c_{m})\alpha_{a_{q}}^{t_{q}}\beta_{a_{q}}^{1-t_{q}}\\
=&\sum_{t_{1},\ldots,t_{m}=0}^{1}\prod_{q=1}^{m}\alpha_{q}^{t_{q}}\beta_{q}^{1-t_{q}}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,x_{q},c_{q},\ldots,c_{m})

@@

%blue} In case of a chain $L=2$ and $N=3$ and choosing $i=2$ this reads as 
%\begin{equation*}
%	D_{22}^{2L-1}=6e_{22}^{tot}+e_{11}^{tot}-e_{22}^{tot}-e_{33}^{tot}-2e_{22}^{tot}e_{22}^{tot}-2e_{23}^{tot}e_{32}^{tot}
%\end{equation*}
%where
%\begin{equation*}
%	e_{ab}^{tot}=e_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes e_{ab}\qquad \forall a,b\in \{1,2,3\}
%\end{equation*}
%This gives exactly
%\begin{equation*}
%	D_{22}^{2L-1}=\left(
%	\begin{array}{ccccccccc}
%		2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 2 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & -2 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & -2 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & -2 & 0 & 0 & 0 \\
%		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & -2 \\
%	\end{array}
%	\right)
%\end{equation*}
%}
%\textbf{Observation}: it seems to me that, although not diagonal, the $D_{ii}^{2L-1}$ does not chaing the exitation of the chain since we have $e_{ij}^{tot}e_{ji}^{tot}$!\\
%The following \textit{lower diagonal} elements of $U_{0}(x)$, $\forall i=2,\ldots,L$ and for $j=1$
%\begin{equation}
%	C_{i}(x)=C_{i}^{2L-1}x^{2L-1}+\ldots
%\end{equation}
%where the coefficient is
%\begin{equation}\label{c}
%	C_{i}^{2L-1}=2e_{1i}^{tot}+2\sum_{a< b}\left(e_{1i}^{[a]}e_{11}^{[b]}-e_{1i}^{[a]}e_{ii}^{[b]}-\sum_{a=2\,:\,k\neq j}^{N}e_{1a}^{[a]}e_{ai}^{[b]}\right)
%\end{equation}
\item For $B_{j}(x)$  $\forall j=1,\ldots,N-1$ 
\begin{equation}\label{B-charge}
		B_{j}^{2L-1}=	2e_{jN}^{tot}e_{NN}^{tot}-2\sum_{a,b=1\,:\, a<b}^{L}\,\sum_{k=1}^{N}e_{kN}^{[a]} e_{jk}^{[b]}
\end{equation}
\begin{comment}
\begin{equation}
B_{j}(x)=B_{j}^{2L-1}x^{2L-1}+\ldots
\end{equation}
where the coefficient is 
\begin{equation}\label{b}
\begin{split}
B_{j}^{2L-1}&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-e_{j1}^{[a]}e_{jj}^{[b]}-\sum_{k=2\,:\,k\neq j}^{N}e_{k1}^{[a]}e_{jk}^{[b]}\right)\\
&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-\sum_{k=2}^{N}e_{k1}^{[a]}e_{jk}^{[b]}\right)
\end{split}
\end{equation}
then
\begin{equation}
\begin{split}
B_{j}^{2L-1}=2e_{j1}^{tot}+
2\sum_{a,b=1\,:\, a<b}^{L}\left(e_{j1}^{[a]}e_{11}^{[b]}\right)-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=2}^{N}\left( e_{jk}^{[a]}e_{k1}^{[b]}\right)
\end{split}
\end{equation}
\begin{equation}
\begin{split}
B_{j}^{2L-1}&=
2\sum_{a,b=1}^{L}\left(e_{j1}^{[a]}e_{11}^{[b]}\right)-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=1}^{N}\left( e_{jk}^{[a]}e_{k1}^{[b]}\right)\\
%	&=
%	2e_{j1}^{tot}e_{11}^{tot}-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=1}^{N} e_{jk}^{[a]}e_{k1}^{[b]}
\end{split}
\end{equation}
Thus
\begin{equation}
\boxed{	B_{j}^{2L-1}=	2e_{j1}^{tot}e_{11}^{tot}-2\sum_{a,b=1\,:\, a>b}^{L}\,\sum_{k=1}^{N} e_{jk}^{[a]}e_{k1}^{[b]}}
\end{equation}
\end{comment}
\item For $D_{i,j}(x)$ with $i,j=2,\ldots,N$ such that $i\neq j$
\begin{equation}
D_{i,j}^{2L}=-2e_{ji}^{tot}
\end{equation}
\end{itemize}
\textbf{Remark}: it is easy to see that, when restricted to the case of 2 species,  \eqref{a2lp},\eqref{a2l},\eqref{a2lm1} correspond to the one compute in \cite{frassek2020eigenstates}. \\ \\
The interesting charges (we only look for the first non trivial one) take the following form

@@

\begin{equation}\label{W-charges-Bad}

@@

To prove this statement we introduce the following notation. We identify each state by 
	|\tau_{1},\ldots,\tau_{L}\rangle\qquad \text{where}\qquad \tau_{x}\in\{1,\ldots,N\}\quad \forall x\in \{1,\ldots,L\}
therefore the vacuum state reads
	|\Psi_{0}^{0}\rangle=|N,\ldots,N\rangle
We first write some relations that will be useful in the proof.
\begin{equation}\label{BActionVoid}
	B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=\sum_{x=1}^{L}2(L-x+1)|N,\ldots,\tau_{x}=i,\ldots,N\rangle
	D_{i,j}^{2L}|\Psi_{0}^{0}\rangle=0
	D_{i,j}^{2L}|\tau_{1},\ldots,\tau_{L}\rangle=-2|\tau_{1}^{'}\ldots,\tau_{L}^{'}\rangle \qquad \text{where}\qquad \tau^{'}_{x}=\begin{cases}
		\tau_{x}\quad &\text{if}\quad \tau_{x}\neq i\\
		j\quad &\text{if}\quad \tau_{x}=i
\begin{equation}\label{GoodRelation}
	D_{i,j}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=-2B_{j}^{2L-1}|\Psi_{0}^{0}\rangle
	D_{i,j}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle&= D_{j,i}\sum_{x=1}^{L}2(L-x+1)|N,\ldots,\tau_{x}=i,\ldots,N\rangle\nonumber
	-2e_{ji}^{tot}\sum_{x=1}^{L}2(L-x+1)|N,\ldots,\tau_{x}=i,\ldots,N\rangle\nonumber
	-4\sum_{x=1}^{L}2(L-x+1)|N,\ldots,\tau_{x}=j,\ldots,N\rangle\nonumber
	-2B_{i}|\Psi_{0}^{0}\rangle
	D_{k,j}^{2L}B_{i}^{L}|\Psi_{0}^{0}\rangle=0\qquad \forall k,j,i\in\{1,\ldots,N-1\}\;:\;k\neq i
	D_{i,i}^{2L}\Psi_{0}^{0}\rangle=-|\Psi_{0}^{0}\rangle \qquad \forall i\in \{1,\ldots,N-1\}
Indeed,
D_{i,i}^{2L}|\Psi_{0}^{0}\rangle=	(2e_{ii}^{tot}-I)|\Psi_{0}^{0}\rangle=-|\Psi_{0}^{0}\rangle
\begin{equation}\label{GainCommutationQ}
	Q_{0}^{2L}|\Psi_{0}^{0}\rangle=(2L+N)(1+L)|\Psi_{0}^{0}\rangle
Therefore, $Q_{0}^{2L}$ acts diagonally on the state $|\Psi_{0}^{0}\rangle$. Indeed,
	Q_{0}^{2L}|\Psi_{0}^{0}\rangle&=\left((N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}+2\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}\right)|\Psi_{0}^{0}\rangle\\&=
		\left((N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}\right)|\Psi_{0}^{0}\rangle
		(N-NL-2L+2(N+1)L+2L^{2})|\Psi_{0}^{0}\rangle
since 
\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}|\Psi_{0}^{0}\rangle=0\qquad e_{NN}^{tot}|\Psi_{0}^{0}\rangle=L|\Psi_{0}^{0}\rangle
Using \eqref{BActionVoid} and \eqref{GainCommutationQ} we have that for all $i,j,k\in\{1,\ldots,N-1\}$
\begin{equation}\label{Three-Relation}
	Q_{0}^{2L}B_{k}^{2L-1}Q_{0}^{2L}B_{j}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=B_{i}^{2L-1}B_{j}^{2L-1}B_{k}^{2L-1}\prod_{j=}^{3}\left(Q_{0}^{2L}-2j(D_{11}^{2L}+D_{NN}^{2L})+4j(j-1)\right)|\Psi_{0}^{0}\rangle
Observe that \eqref{Three-Relation} also implies that 
	Q_{0}^{2L}B_{i}^{2L-1}Q_{0}^{2L}B_{j}^{2L-1}|\Psi_{0}^{0}\rangle=Q_{0}^{2L}B_{i}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle
i.e. $Q_{0}^{2L}B_{i}^{2L-1}$ and $Q_{0}^{2L}B_{j}^{2L-1}$ do commute. This simplify formula \eqref{W-charges-Bad} as
	W|\Psi_{0}^{0}\rangle=&\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}}^{L}\mathbbm{1}_{\{k_{1}+\ldots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots \Delta_{N-1}^{k_{N-1}}\binom{k_{1}+\ldots+k_{N-1}}{k_{1},\ldots,k_{N-1}}\\&\left\{\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{1}\right\}^{k_{1}}\cdots\;\left\{\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{N-1}\right\}^{k_{N-1}}|\Psi_{0}^{0}\rangle
Therefore, we can generalize \eqref{Three-Relation} and find 
		W|\Psi_{0}^{0}\rangle =&\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}}^{L}\mathbbm{1}_{\{k_{1}+\ldots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots \Delta_{N-1}^{k_{N-1}}\binom{k_{1}+\ldots+k_{N-1}}{k_{1},\ldots,k_{N-1}}\\&
		\left(B_{1}^{2L-1}\right)^{k_{1}}\cdots\left( B_{N-1}^{2L-1}\right)^{k_{N-1}}\prod_{j=1}^{k_{1}+\ldots k_{N-1}}\left\{(\Lambda_{0}+\epsilon)-Q_{0}^{2L}+2j(D_{1,1}^{2L}+D_{N,N}^{2L})-4j(j-1)\right\}^{-1}|\Psi_{0}^{0}\rangle
	\binom{k_{1}+\ldots+k_{N-1}}{k_{1},\ldots,k_{N-1}}=\frac{	(k_{1}+\ldots+k_{N-1})!}{k_{1}!\cdots k_{N-1}}
This can be written as
		|\Psi^{''}\rangle=&	\;W|\Psi_{0}^{0}\rangle =\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}}^{L}\mathbbm{1}_{\{k_{1}+\ldots+k_{N-1}\leq L\}}\frac{\Delta_{1}^{k_{1}}\cdots \Delta_{N-1}^{k_{N-1}}}{k_{1}!\cdots k_{N-1}!}\\&
		\left(\frac{B_{1}^{2L-1}}{2^{k_{1}}}\right)^{k_{1}}\cdots\left( \frac{B_{N-1}^{2L-1}}{2^{k_{N-1}}}\right)^{k_{N-1}}\frac{\Gamma\left(e_{NN}^{tot}+2-(k_{1}+\ldots+k_{N-1})\right)}{\Gamma\left(e_{NN}^{tot}+2\right)}|\Psi_{0}^{0}\rangle
